Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
abstracting CEK1 k
fill in missing reduction rules in CEK1
minor fix on grammar

@@

	\stxrule{\kappa}{continuations}{
		\mathtt{stop} \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa \mid
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
	}
	\stxrulecont{	
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
		\langle c \rangle \kappa
	}
	\end{array}
	\]

	Reduction \fbox{$ \judgeDCreduce{s}{s} $}
	\[
	\begin{array}{rclr}

	& \dots  \\
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			} \; \kappa)}
	}{
		\sOOreturn{v_1}{
			\langle\cOOcast{T_3}{l}{T_1}\rangle
			(\mathtt{app_2} \; v_2 \; 
			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
	}{}

	%	\redrule{
	%		\sOOreturn{v}{(
	%			\mathtt{app_2} \;
	%			(\vOOfun{\rho}{x}{e}) \;
	%			\kappa
	%		)}
	%	}{\sOOinspect{e}{\rho{}[x := v]}{\kappa}}{}

	\redrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{(\mathtt{fst} \; \kappa)}
	}{
		\sOOreturn{v}{(
			\mathtt{fst} \;
			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
			)}
	}{}

@@

	\redrule{
		\sOOreturn{v_3}{(
			\mathtt{case_3} \;
			v_1 \; v_2 \;
			\kappa
			)}
	}{case(v_1,
		\mathtt{app_2} \; v_2 \; \kappa,
		\mathtt{app_2} \; v_3 \; \kappa
		)}{}

@@

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
		\sOOhalt{(\oOOblame{l})}
		\\ &
	}{
		\sidecond{applyCast(c,v) = \rOOfail{l}}
	}
	\end{array}
	\]

@@

\todo[inline]{Please fill in the missing reduction rules. -JS}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    }

@@

	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
	}
	\stxrulecont{
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}
	\stxrule{\kappa}{continuation}{
		(c,k)
	}
	\stxrule{k}{pre-continuations}{
		\hckOOmt \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa
	}
	\stxrulecont{
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
	}
	\end{array}
	\]

	Build continuation \fbox{$ cont(k) = \kappa $}
	\[
	\begin{array}{rclc}
	\funrule{cont(k)}{(id(T_1),k)}{
		\sidecond{k : T_1 \Longrightarrow T_2}}
	\end{array}
	\]

	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
	\[
	\begin{array}{rclc}
	\funrule{ext(c_1,(c_2,k))}{(seq(c_1,c_2),k)}{}
	\end{array}
	\]

@@

\todo[inline]{In the definition of values, there is a ``b'' in the fun
  case. I don't see any definitions of a nonterminal ``b''.
  Perhaps you meant ``e''. -JS}
\todo[inline]{In the grammars for values and pre-continuations,
   remove all the subscripts on c's and v's. -JS}
\todo[inline]{Change the syntax $(c,k)$ for continuations to
  $\langle c \rangle$ k. -JS}

>>>>

\newcommand{\kOOmt}[0]{\mathtt{stop}}
\newcommand{\kOOconsI}[3]{\mathtt{cons_1} \; #1 \; #2 \; #3}
\newcommand{\kOOconsII}[2]{\mathtt{cons_2} \; #1 \; #2}
\newcommand{\kOOinl}[1]{\mathtt{inl} \; #1}
\newcommand{\kOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\kOOappI}[3]{
	\mathtt{app_1} \; #1 \; #2 \; #3
}
\newcommand{\kOOappII}[2]{
	\mathtt{app_2} \; #1 \; #2}
\newcommand{\kOOcar}[1]{
	\mathtt{fst} \; #1}
\newcommand{\kOOcdr}[1]{
	\mathtt{snd} \; #1}
\newcommand{\kOOcaseI}[4]{
	\mathtt{case_1} \; #1 \; #2 \; #3 \; #4}
\newcommand{\kOOcaseII}[4]{
	\mathtt{case_2} \; #1 \; #2 \; #3 \; #4}
\newcommand{\kOOcaseIII}[3]{
	\mathtt{case_3} \; #1 \; #2 \; #3}
\newcommand{\kOOcast}[2]{
	\langle #1 \rangle #2}

@@

	\stxrule{\kappa}{continuations}{
		\kOOmt \mid
		\kOOconsI{e}{\rho}{\kappa} \mid
		\kOOconsII{v}{\kappa} \mid
		\kOOinl{\kappa} \mid
		\kOOinr{\kappa}
	}
	\stxrulecont{
		\kOOappI{e}{\rho}{\kappa} \mid
		\kOOappII{v}{\kappa} \mid
		\kOOcar{\kappa} \mid
		\kOOcdr{\kappa} \mid
		\kOOcaseI{e_1}{e_2}{\rho}{\kappa}
	}
	\stxrulecont{	
		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
		\kOOcaseIII{v_1}{v_2}{\kappa} \mid
		\kOOcast{c}{\kappa}
	}
	\end{array}
	\]

	Reduction \fbox{$ \judgeDCreduce{s}{s} $}
	\[
	\begin{array}{rclr}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho[x]}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redrule{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
	}{}
	\redrule{
	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}
\redrule{
\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
\sOOinspect{e}{\rho}{(\kOOcar{\kappa})}}{}
\redrule{
	\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
	\sOOinspect{e}{\rho}{(\kOOcdr{\kappa})}}{}
\redrule{
\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
\sOOinspect{e_1}{\rho}{(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}

\redrule{
\sOOreturn{v_1}{(\kOOconsI{\rho}{e_2}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
\sOOreturn{(\vOOcons{v_1}{v_2})}{\kappa}}{}

\redrule{
\sOOreturn{v}{(\kOOinl{\kappa})}}{
\sOOreturn{(\vOOinl{v})}{\kappa}}{}

\redrule{
\sOOreturn{v}{(\kOOinr{\kappa})}}{
\sOOreturn{(\vOOinr{v})}{\kappa}}{}

\redrule{
\sOOreturn{v_1}{(\kOOappI{\rho}{e_2}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa})}}{
\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
	\redrule{
		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			} \; \kappa)}
	}{
		\sOOreturn{v_1}{
			\langle\cOOcast{T_3}{l}{T_1}\rangle
			(\mathtt{app_2} \; v_2 \; 
			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
	}{}
	\redrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{(\mathtt{fst} \; \kappa)}
	}{
		\sOOreturn{v}{(
			\mathtt{fst} \;
			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
			)}
	}{}

@@

\redrule{
\sOOreturn{v_1}{(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOcaseII{E}{v_1}{e_3}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOcaseII{\rho}{v_1}{e_3}{\kappa})}}{
\sOOinspect{e_3}{\rho}{
	(\kOOcaseIII{v_1}{v_2}{\kappa})
}}{}	
		\redrule{
		\sOOreturn{v_3}{(
			\mathtt{case_3} \;
			v_1 \; v_2 \;
			\kappa
			)}
	}{case(v_1,
		\mathtt{app_2} \; v_2 \; \kappa,
		\mathtt{app_2} \; v_3 \; \kappa
		)}{}

@@

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
		\sOOhalt{(\oOOblame{l})}
		\\ &
	}{
		\sidecond{applyCast(c,v) = \rOOfail{l}}
	}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v)}}{}
	\end{array}
	\]

@@

\todo[inline]{Please fill in the missing reduction rules. -JS
\\---\\ Fixed -KC}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    }

@@

	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
		\hcvOOcons{v}{c}{v}{c}
	}
	\stxrulecont{
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}
	\stxrule{\kappa}{continuation}{
		\langle c \rangle k
	}
	\stxrule{k}{pre-continuations}{
		\hckOOmt \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa
	}
	\stxrulecont{
		\mathtt{case_1} \; e \; e \; \rho \; \kappa \mid
		\mathtt{case_2} \; v \; e \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v \; v \; \rho \; \kappa
	}
	\end{array}
	\]

	Build continuation \fbox{$ cont(k) = \kappa $}
	\[
	\begin{array}{rclc}
	\funrule{cont(k)}{\langle id(T_1) \rangle k}{
		\sidecond{k : T_1 \Longrightarrow T_2}}
	\end{array}
	\]

	Extend continuation \fbox{$ ext(c,\kappa) = \kappa $}
	\[
	\begin{array}{rclc}
	\funrule{ext(c_1,\langle c_2 \rangle k)}{\langle seq(c_1,c_2) \rangle k}{}
	\end{array}
	\]

@@
